\bf Hierarchical Forecasts Reconciliation

### 2019-07-01 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
removed line to make pdflatex work
rewriting of unbiasedness preserving property

%&latex
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

@@

@@

	While such a definition is completely serviceable, it obscures the full generality of the methodologies developed in the literature on hierarchical time series.  There are only two important characteristics of the data that we are interested in; the first is that they are multivariate, the second is that they adhere to linear constraints.  Below we provide definitions that provide geometric intuition behind the data and methodologies employed in the hierarchical forecasting.

@@

	 \begin{definition}[Coherent subspace]\label{def:cohspace}
	 	The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which a set of linear constraints hold for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
	 \end{definition}

     To further illustrate, Figure \ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.  The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space, i.e. $m=2$ and $n=3$.  It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$.  In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.  However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom level series, $y_{A,t}$ and $y_{B,t}$. In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$, which also span the coherent subspace.  Thus, while there are multiple ways to define a hierarchy and an associated `$\bm{S}$ matrix', the columns of any `$\bm{S}$ matrix' will always span the same unique coherent subspace.

@@

	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.   In fact, the term {\em hierarchical} is misleading since the literature has covered instances that cannot easily be depicted as hierarchies as in Figure~\ref{fig:basichier}.  These include \todo{include references}.  Furthermore, although the definition makes clear reference to time series, this definition can be easily generalised to any vector-valued data for which some constraints are known to hold.

@@

    Without any loss of generality, that above definition could also be applied to prediction for multivariate data in general, rather than just forecasting of time series.  While the observed data will be coherent by definition, it is important to note that there are a number of reasons why forecasts or predictions may be incoherent.  First, since applications of hierarchical forecasting tend to be very high dimensional a common strategy in practice is to produce forecasts for each time series independently using univariate models.  Second, even where a multivariate model is used for the full vector of observations, it may be difficult to capture the linear constraints inherent in the data particularly for complicated non-linear models.  Third, in some cases judgemental adjustments may be made inducing incoherent forecasts.

@@

	As discussed in the previous section, for a number of reasons, coherence is not guaranteed when forecasts are produced for all series.To ensure aligned decision making, it is desirable to adjust forecasts ex post to endure coherence.  This process is referred to as {\em reconciliation}.  In the most general terms, reconciliation can be defined as follows

@@

	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, and with few exceptions, these belong more specifically to the class of projections.  This involves pre-multiplying $\hat{\bm{y}}_{t+h|t}$ by a projection matrix that can be written down in a number of ways.  In \todo{references}, the projection matrix is written in the form $\bm{SG}$ (with $\bm{P}$ used in place of $\bm{G}$ in some cases).  This facilitates an interpretation of reconciliation as a two-step process, in the first step base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.  It should be noted that if $\bm{G}$ is set arbitrarily, then $\bm{SG}$ will not necessarily be a projection.  However for a large class of reconciliation methods, $\bm{G}$ is determined by treating forecast reconciliation as a problem in linear regression model.  In this case least squares estimators result in values of $\bm{G}$ that do in fact imply that $\bm{SG}$ is a projection.

%	\subsection{Reconciliation in general}\label{sec:reconciliation}
%
%	
%	As discussed, reconciliation is distinct from coherence, since the former refers to a process whereby incoherent forecasts are made coherent. Although reconciliation methods for point forecasts are extant in the literature they are rarely defined explicitly.  We do so here in slightly more general terms than usual. 
%	%We then extend this idea to the novel concept of probabilistic reconciliation.
%	
%	Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ conditional on information up to and including time $t$. We now introduce a linear function that converts unreconciled forecasts into new bottom level forecasts.
%	Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively, and let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})=\bm{G}\bm{y}+\bm{d}$.  A composition of $g$ and $s(.)$ gives the following definition for point forecast reconciliation.
%	
%	\begin{definition}\label{def:reconpoint}
%		The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $g(.)$ iff
%		\begin{equation}
%		\tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{G}\hat{\bm{y}}_{t+h|t}+\bm{d})\,.
%		\end{equation}
%	\end{definition}

%	\begin{table}[!h]
%		\caption{Summary of reconciliation methods that are projections. Here, $\hat{\bm{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, $\hat{\bm{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}, $\hat{\bm{W}}^{wls}$ is the diagonal matrix with diagonal elements $w_{ii}$, and $\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$, where $w_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{W}}^{sam}$.}\label{table:2}
%		\centering
%		\begin{tabular}{lll}
%			\toprule
%			\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
%			\midrule
%			OLS             &
%			$\bm{I}$  &
%			$\bm{S}'$  \\
%			MinT(Sample)    &
%			$\hat{\bm{W}}^{sam}$ &
%			$\bm{S}'(\hat{\bm{W}}^{sam})^{-1}$ \\
%			MinT(Shrink)    &
%			$\tau\text{Diag}(\hat{\bm{W}}^{sam}) + (1-\tau)\hat{\bm{W}}^{sam}$ &
%			$\bm{S}'(\hat{\bm{W}}^{shr})^{-1}$ \\
%			WLS       &
%			$\text{Diag}(\hat{\bm{W}}^{shr})$ &
%			$\bm{S}'(\hat{\bm{W}}^{wls})^{-1}$ \\
%			\bottomrule
%		\end{tabular}
%	\end{table}
%	
%	
%	\begin{figure}
%		\input{Figs/pointforerec_schematic.tex}
%		\caption{Summary of probabilistic point reconciliation. The mapping $s\circ g$ projects the unreconciled forecast $\hat{\bm{y}}_{t+h|h}$ onto $\mathfrak{s}$, yielding the reconciled forecast $\tilde{\bm{y}}_{t+h|h}$ with subscripts dropped in the figure for ease of presentation. Since the smallest hierarchy involves three dimensions, this figure is only a schematic.}\label{fig:pointfr_sch}
%	\end{figure}
%	
%	The columns of $\bm{S}$ and $\bm{R}$ provide a basis for $\mathbb{R}^n$. Therefore any incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$. Let $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$ respectively, after a change of basis. The process of reconciliation involves setting the values of the reconciled bottom-level series to be $\tilde{\bm{b}}_{t+h|t}$, and ignoring $\tilde{\bm{a}}_{t+h|t}$ to ensure coherence. From properties of linear algebra it follows that
%	\[
%	\hat{\bm{y}}_{t+h|t} = (\bm{S} ~ \bm{R})
%	\begin{pmatrix}
%	\tilde{\bm{b}}_{t+h|t}\\ \tilde{\bm{a}}_{t+h|t}
%	\end{pmatrix}= \bm{S}\tilde{\bm{b}}_{t+h|t} + \bm{R}\tilde{\bm{a}}_{t+h|t},
%	\]
%	while the reconciled point forecast is
%	\[
%	\tilde{\bm{y}}_{t+h|t} = \bm{S}\tilde{\bm{b}}_{t+h|t}.
%	\]
%	
%	
%	In order to find $\tilde{\bm{b}}_{t+h|t}$ we require the inverse $(\bm{S} ~ \bm{R})^{-1}$ which is given by
%	\begin{equation}
%	(\bm{S} ~ \bm{R})^{-1} = \begin{pmatrix}
%	(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
%	\end{pmatrix}\,,
%	\end{equation}
%	where $\bm{S}_{\bot}$ is the orthogonal complements of $\bm{S}$. Thus it follows that $\tilde{\bm{b}}_{t+h|t}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$. Here $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ corresponds to $\bm{G}$ as defined previously.

	\subsection{Motivation of using projections}

	We have seen from the above discussion that projection is playing an important role in point forecast reconciliation. Now we turn our attention to the following two theorems that explains the motivation of using projection in this context.

	First, let $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ and assume $\hat{\bm{y}}_{t+h|t}$ is an unbiased prediction; that is $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.

	\begin{theo}[Unbiasedness preserving property]
		For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also an unbiased prediction as long as $s\circ g$ is a projection onto $\mathfrak{s}$.
	\end{theo}
	\begin{proof}
		The expected value of the reconciled forecast is given by
		\[
		\E_{1:t}(\tilde{\bm{y}}_{t+h|t})
		= \E_{1:t}(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t})
		= \bm{S}\bm{G}\E_{1:t}(\hat{\bm{y}}_{t+h|t})
		= \bm{S}\bm{G}\bm{\mu}_{t+h|t}.
		\]
		Since the aggregation constraints hold for the true data generating process, $\bm{\mu}_{t+h|t}$ must lie in $\mathfrak{s}$. If $\bm{S}\bm{G}$ is a projection, then it is equivalent to the identity map for all vectors that lie in its range. Therefore $\bm{S}\bm{G}\bm{\mu}_{t+h|t}=\bm{\mu}_{t+h|t}$ when $\bm{S}\bm{G}$ is a projection matrix.
	\end{proof}

	We note the above result holds when the projection $s\circ g$ is only onto the coherent subspace $\mathfrak{s}$. That is the result does not hold for any general $g$ even when the range of $s\circ g$ is $\mathfrak{s}$. To describe this more explicitly suppose $s\circ g$ is a projection to any linear subspace $\mathfrak{L}$ of $\mathfrak{s}$. Then $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$ as the projection will move $\bm{\mu}_{t+h|t}$ to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$ as depicted in the Figure \ref{fig:Schematic_3D}. Thus $\E_{1:t}(\tilde{\bm{y}}_{t+h|t}) \ne \bm{\mu}_{t+h|t}$ which breaks the unbiasedness. Recall the top-down method \citep{Gross1990} with 
	\begin{equation}\label{eq:top-downG}
	\bm{G}=\begin{pmatrix}
	\bm{p} & \bm{0}_{(m \times n-1)}
	\end{pmatrix}
	\end{equation}
    where $\bm{p} = (p_1,\dots,p_m)'$ is an $m$-dimensional vector consisting a set of proportions which is use to disaggregate the top-level forecasts along the hierarchy. \cite{Hyndman2011} claimed that this method is not producing unbiased coherent forecasts even if the base forecasts are unbiased since $\bm{SGS} \ne \bm{S}$ for $\bm{G}$ in (\ref{eq:top-downG}). However the more rational explanation is that, in top-down approach the projection $s\circ g$ is not onto $\mathfrak{s}$, but to a linear subspace of $\mathfrak{s}$ spanned by $\bm{p}$. Thus from above explanation it follows that  $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$ and hence not producing unbiased forecasts.

@@

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

@@

\theoremstyle{property}
\newtheorem{property}{Property}[section]

@@

	While such a definition is completely serviceable, it obscures the full generality of many methodologies developed in the literature on so-called hierarchical time series.  In fact, to apply concepts such as coherence and reconciliation, the data only require two important characteristics; the first is that they are multivariate, the second is that they adhere to linear constraints.  Below we redefine the concepts of coherence and hierarchical time series using a geometric interpretation, before turning our attention to forecast reconciliation in Section~\ref{sec:Reconciliation}.

@@

	 \begin{definition}[Coherent subspace]\label{def:cohspace}
	 	The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which a set of linear constraints holds for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
	 \end{definition}

     To further illustrate, Figure \ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.  The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space, i.e. $m=2$ and $n=3$.  It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$.  In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.  However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom level series, $y_{A,t}$ and $y_{B,t}$. In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$.  However, while there are multiple ways to define an $\bm{S}$ matrix, in all cases the columns will span the same coherent subspace, which is unique.

@@

	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.   In fact, the term {\em hierarchical} is misleading since the literature has covered instances that cannot easily be depicted as hierarchies as in Figure~\ref{fig:basichier}.  These include \todo{include references}.  Furthermore, although the definition makes clear reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.

@@

    Without any loss of generality, that above definition could also be applied to prediction for multivariate data in general, rather than just forecasting of time series.  While the observed data will be coherent by definition, it is important to note that there are a number of reasons why forecasts or predictions may be incoherent.  \todo{some discussion about why reconciliation v single level}

    First, since applications of hierarchical forecasting tend to be very high dimensional a common strategy in practice is to produce forecasts for each time series independently using univariate models.  Second, even where a multivariate model is used for the full vector of observations, it may be difficult to capture the linear constraints inherent in the data particularly for complicated non-linear models.  Third, in some cases judgemental adjustments may be made inducing incoherent forecasts.

@@

	As discussed in the previous section, for a number of reasons, coherence is not guaranteed when forecasts are produced for all series.  To ensure aligned decision making, it is desirable to adjust forecasts ex post to ensure coherence.  This process is referred to as {\em reconciliation}.  In the most general terms, reconciliation can be defined as follows

@@

	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.  In \todo{references}, this matrix is written in the form $\bm{SG}$ (with $\bm{P}$ used in place of $\bm{G}$ in some cases), where $\bm{G}$ is an $(n-m)\times n$ matrix.  This facilitates an interpretation of reconciliation as a two-step process, in the first step base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.

	\subsection{Unbiasedness preserving property}

	A sensible property is that reconciliation should not change base forecasts that are already coherent.  That is 
	\begin{equation}	
	\label{eq:propcohnochange}
	\tilde{\bm{y}}_{t+h|t}=\bm{SG}\hat{\bm{y}}_{t+h|t}=\hat{\bm{y}}_{t+h|t}\mbox{ iff }
	\hat{\bm{y}}_{t+h|t}\in\mathfrak{s}\,.
	\end{equation}

	Using geometric intuition, it should be clear that the property in Equation~\ref{eq:propcohnochange} will hold when $\bm{SG}$ is a projection matrix \todo{perhaps find a reference - it is so fundamental that is is on wikipedia and wolfram mathworld}.  This also implies that the the property in Equation~\ref{eq:propcohnochange} does not hold for arbitrary $\bm{G}$.  For this reason it is often assumed that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.  Enforcing these assumptions are equivalent to assuming that  $\bm{SG}$ is a projection matrix.\todo{perhaps elaborate in a proof in appendix}

	The property that projections map all vectors in the coherent subspace onto themselves is useful in proving the unbiasedness preserving property of reconciliation, previously proven by\todo{reference Shanika and maybe van Erven Culigari}.  Suppose that the target of a point forecast is $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ where the expectation is taken over the predictive density.  Our point forecast is an estimate of this quantity that is random due to sampling variation.  The point forecast will be unbiased if $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.

	\begin{theo}[Unbiasedness preserving property]
		For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also an unbiased prediction as long as $\bm{SG}$ is a projection onto $\mathfrak{s}$.
	\end{theo}
	\begin{proof}
		The expected value of the reconciled forecast is given by
		\[
		\E_{1:t}(\tilde{\bm{y}}_{t+h|t})
		= \E_{1:t}(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t})
		= \bm{S}\bm{G}\E_{1:t}(\hat{\bm{y}}_{t+h|t})
		= \bm{S}\bm{G}\bm{\mu}_{t+h|t}.
		\]
		Since $\bm{\mu}_{t+h|t}$ is an expectation taken with respect to the degenerate predictive density it must lie in $\mathfrak{s}$. We have already established that when $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$ then it maps all vectors in $\mathfrak{s}$ onto themselves. As such $\bm{S}\bm{G}\bm{\mu}_{t+h|t}=\bm{\mu}_{t+h|t}$ when $\bm{S}\bm{G}$ is a projection matrix.
	\end{proof}

	We note that the above result holds when the projection $\bm{SG}$ is only onto the coherent subspace $\mathfrak{s}$ and not for all projection matrices in general. To describe this more explicitly suppose $\bm{SG}$ has as its image  $\mathfrak{L}$ which is itself a a lower dimensional linear subspace of $\mathfrak{s}$, i.e. $\mathfrak{L}\subset\mathfrak{s}$. Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$,  $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$. This is depicted in Figure~\ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.  Therefore in this case, the reconciled forecast will have as its expectation $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and be biased.  This result has implications in practice, in particular, the top-down method \citep{Gross1990} has 
	\begin{equation}\label{eq:top-downG}
	\bm{G}=\begin{pmatrix}
	\bm{p} & \bm{0}_{(m \times n-1)}
	\end{pmatrix}
	\end{equation}
    where $\bm{p} = (p_1,\dots,p_m)'$ is an $m$-dimensional vector consisting a set of proportions which is use to disaggregate the top-level forecasts along the hierarchy.  In this case it can be verified that $\bm{SG}$ is idempotent, i,e. $\bm{SGSG}=\bm{SG}$ and therefore $\bm{SG}$ is a projection matrix.  However the image of this projection is not an $m$-dimensional subspace but a $1$-dimensional subspace.  As such, top-down reconciliation will bias base forecasts when those base forecasts are unbiased.

@@

	\subsection{Why do projections work?}
